Validation failed EVT

### 2022-07-26 analysis/article-results.Rmd
First versio with nomogram

split(imps_combined, ~ .imp) |> 
  map(.f = ~ glm(update(model_formula, . ~ . * dataset), family = binomial, data = .x)) |> 
  mice::pool() |> 
  broom::tidy() |>  
  ggforestplot::forestplot(
    name = term,
    estimate = estimate,
    se = std.error
  )

split(imps_combined, ~ .imp) |> 
  map(.f = ~ glm(update(model_formula, . ~ . * dataset), family = binomial, data = .x)) |> 
  mice::pool() |> 
  broom::tidy() |> 
  select(term, estimate)

split(imps_combined |> filter(dataset == "develop"), ~ .imp) |> 
  map(.f = ~ glm(model_formula, family = binomial, data = .x)) |> 
  mice::pool() |> 
  broom::tidy() |> 
  pull(estimate)

cbind.data.frame(
  split(imps_combined, ~ .imp) |> 
  map(.f = ~ glm(update(model_formula, . ~ . * dataset), family = binomial, data = .x)) |> 
  mice::pool() |> 
  broom::tidy() |> 
  select(term, estimate),
  "develop" = split(imps_combined |> filter(dataset == "develop"), ~ .imp) |> 
  map(.f = ~ glm(model_formula, family = binomial, data = .x)) |> 
  mice::pool() |> 
  broom::tidy() |> 
  pull(estimate),
  "valid" =  split(imps_combined |> filter(dataset == "valid"), ~ .imp) |> 
  map(.f = ~ glm(model_formula, family = binomial, data = .x)) |> 
  mice::pool() |> 
  broom::tidy() |> 
  pull(estimate),
  "combined" =  split(imps_combined, ~ .imp) |> 
  map(.f = ~ glm(model_formula, family = binomial, data = .x)) |> 
  mice::pool() |> 
  broom::tidy() |> 
  pull(estimate)
) |> 
  View()

# ORs
cbind.data.frame(
  split(imps_combined, ~ .imp) |> 
  map(.f = ~ glm(update(model_formula, . ~ . * dataset), family = binomial, data = .x)) |> 
  mice::pool() |> 
  broom::tidy(exponentiate = TRUE) |> 
  select(term, estimate),
  "develop" = split(imps_combined |> filter(dataset == "develop"), ~ .imp) |> 
  map(.f = ~ glm(model_formula, family = binomial, data = .x)) |> 
  mice::pool() |> 
  broom::tidy(exponentiate = TRUE) |> 
  pull(estimate),
  "valid" =  split(imps_combined |> filter(dataset == "valid"), ~ .imp) |> 
  map(.f = ~ glm(model_formula, family = binomial, data = .x)) |> 
  mice::pool() |> 
  broom::tidy(exponentiate = TRUE) |> 
  pull(estimate),
  "combined" =  split(imps_combined, ~ .imp) |> 
  map(.f = ~ glm(model_formula, family = binomial, data = .x)) |> 
  mice::pool() |> 
  broom::tidy(exponentiate = TRUE) |> 
  pull(estimate)
) |> 
  View()

model.matrix(model_formula, data=imps_combined) %>% 
  cor(use="pairwise.complete.obs") %>% 
  ggcorrplot::ggcorrplot(show.diag = F, type="lower", lab=TRUE, lab_size=2)
```

@@

# Print penalied model coefficients
knitr::kable(data.frame(mod_coefs_comb))

validation_comb_lambdamin$validation_summary
validation_comb_lambdamin$validation_df |> 
  ggplot(aes(x = corrected)) +
  geom_histogram(bins = 50) +
  facet_wrap(~ measure, scales = "free")

validation_comb_lambdamin$validation_df |> 
  group_by(boot_num) |> 
  summarise(pen = mean(penalty)) |>
  #pull(pen) |>  mean()
  ggplot(aes(pen)) +
  geom_histogram()

@@

>>>>

inter_model <- split(imps_combined, ~ .imp) |> 
  map(.f = ~ glm(update(model_formula, . ~ . * dataset), family = binomial, data = .x)) |> 
  mice::pool() |> 
  broom::tidy()

summ_inter <- cbind.data.frame(
  inter_model |>  
    filter(str_detect(term, pattern = "valid$", negate = TRUE)) |> 
    select(term),
  "development" = inter_model |>  
    filter(str_detect(term, pattern = "valid$", negate = TRUE)) |> 
    pull(estimate),
  "interaction" = inter_model |>  
    filter(str_detect(term, pattern = "valid$")) |> 
    pull(estimate),
  "pval_interaction" = inter_model |>  
    filter(str_detect(term, pattern = "valid$")) |> 
    pull(p.value)
) |> 
  mutate(
    validation = development + interaction
  ) |> 
  mutate(across(where(is.numeric), ~ round(.x, 3)))

DT::datatable(
  summ_inter,
  extensions = 'Buttons',
  options = list(
    dom = 'Blfrtip', 
    buttons = c('csv', 'excel', 'pdf'),
    lengthMenu = list(c(10, 25, 50, -1), c(10, 25, 50, "All"))
  )
)
```

@@

# Print penalised model coefficients
DT::datatable(
  data.frame(round(mod_coefs_comb, digits = 3)),
  extensions = 'Buttons',
  options = list(
    dom = 'Blfrtip', 
    buttons = c('csv', 'excel', 'pdf'),
    lengthMenu = list(c(10, 25, 50, -1), c(10, 25, 50, "All"))
  )
)

# Optimism corrected
validation_comb_lambdamin$validation_summary %>% 
  filter(measure %in% c("auc", "intercept", "slope")) %>% 
  group_by(measure) %>% 
  summarise(value = paste0(corrected, " [", lower_corrected, ";", upper_corrected, "]")) %>%
  knitr::kable()

@@

```{r nomogram}
# Make data for nomogram labels
dat_nomogram <- imps_combined %>% 
  select(all_of(c(response_var, candidate_predictors))) %>% 
  mutate(
    InnCca_nr_90orLarger = factor(
      InnCca_nr_90orLarger,
      levels = levels(InnCca_nr_90orLarger),
      labels = c("0", ">=1")
    ),
    ICAE_NASCET_Degree = factor(
      ICAE_NASCET_Degree,
      levels = levels(ICAE_NASCET_Degree),
      labels = c("<99", ">=99")
    )
  )

# Set variable labels
Hmisc::label(dat_nomogram$M_age) <- "Age (decades)"
Hmisc::label(dat_nomogram$M_prev_ht) <- "Hypertension"
Hmisc::label(dat_nomogram$AorticVariant) <- "Aortic variant"
Hmisc::label(dat_nomogram$ArchElongation) <- "Arch Elongation"
Hmisc::label(dat_nomogram$AngleFollowingBifurcation) <- "Angle post-bifurcation"
Hmisc::label(dat_nomogram$InnCca_nr_90orLarger) <- "CCA angles >=90 degr."
Hmisc::label(dat_nomogram$ICAE_NASCET_Degree) <- "ICA stenosis"

dd <- datadist(dat_nomogram)
options(datadist = "dd")

# Edit some labels
mod_lrm <- lrm(model_formula, data = dat_nomogram)
mod_lrm$coefficients <- setNames(unname(drop(mod_coefs_comb)), names(mod_lrm$coefficients))

par(mar = c(2,2,1,1))
nom <- nomogram(
  fit = mod_lrm, 
  fun = plogis, 
  maxscale = 10, 
  funlabel = "Predicted probability", 
  lp = FALSE, 
  fun.at = c(.01, .05, seq(.1, 1, by = .1))
)

plot(nom)

# Get max probability in combined dataset?
```
